\section[Conclusions]{Conclusions}

\begin{frame}{Conclusions}
	\begin{itemize}
		\item We have seen how to determine confidence intervals and prediction regions using the theory of linear and logistic regressions.
		\pause
		\item We have shown that for linear and logistic regressions, the core of the calculation for intervals and regions is the covariance matrix of $\hat{\beta}$, which is determined from all the training data. This matrix is used regardless of the inputs $X_i$ subsequently provided to the model.
		\pause
		\item We also estimated these same intervals and regions using a bootstrapping algorithm.
		\pause
		\item We observed a strong agreement between the theoretical results and the bootstrapping method.
		\pause
		\item We also saw that the prediction region is a much more demanding metric than the ROC curve for classification.
	\end{itemize}
\end{frame}

\begin{frame}{Conclusions}
	\begin{itemize}
		\item Although the bootstrapping algorithm was used here for linear and logistic regressions, it remains applicable \textbf{to any} regression and classification model.
		\pause
		\item For the majority of models, we do not have theoretical frameworks to determine these intervals and regions; therefore, empirical methods are the only ones available. However, they require training multiple models, which can be \textbf{computationally expensive}.
		\pause
		\item The confidence interval provides an estimate of the model \textbf{variance}.
		\pause
		\item The prediction region encompasses the \textbf{sum of all errors} (Bayes error, approximation error or bias, and estimation error or variance) but does not allow for discriminating between approximation error and Bayes error.
	\end{itemize}
\end{frame}

\begin{frame}{Conclusions}
	\begin{itemize}
		\item Prediction regions are \textbf{major} tools for validating machine learning models used in \textbf{safety-critical} systems.
		\pause
		\item \textbf{Conformal prediction} methods have been developed more recently to statistically \textbf{guarantee} coverage for prediction regions and are applicable to all regression and classification models.
	\end{itemize}
\end{frame}
